### 2015-04-08 related.tex
Simplified comparision with Indigo

Since eventual consistency alone is insufficient to build correct applications,
several systems~\cite{Bayou,Pileus,RedBlue} propose a lattice of stronger
consistency levels. Similarly, traditional database processing
systems~\cite{Berenson95} and their replicated variants~\cite{BailisHAT}
propose weaker isolation levels for performance. In these systems, the onus is
on the developer to choose the correct consistency(isolation) level for
operations(transactions). \name relieves the developer of this burden, and
instead expects programmers to declare application-specific consistency
requirements as first-order formulas. In this regard, \name is similar to Indigo
\cite{indigo}, which requires programmers to declare application-specific
invariants that are expected to be met, along with pre- and post-conditions on
operations as formulas in first-order logic. Indigo then performs a static
analysis on formulas to identify $I$-offender sets - sets of operations,
which, when performed concurrently, result in violation of one or more of the
stated invariants. For each offending set of operation, if programmer chooses
invariant-violation avoidance over violation repair, the system employs various
techniques, such as escrow reservation, to ensure that the offending set of
operations are never run concurrently.

While serializing operations is sufficient to ensure that the application state
never violates invariants (e.g: \cf{balance $\ge$ 0}), there exist a range of
desirable application-level properties, which cannot be captured in Indigo's
specification language, or for which serialization is an overkill. For instance,
it is neither efficient nor straightforward in Indigo to declare and enforce a
condition to prevent the missing update anomaly
(Figure~\ref{fig:missingUpdateAnomaly}) in the bank account application. The
only way is to encode specifications of all bank account operations such that
every pair of operations are identified as $I$-offending, for some invariant
($I$), resulting in them being serialized. In contrast, \name's contract
language allows for precise encoding of the desired property, and the contract
classification scheme ensures that the it can be enforced without the need to
serialize operations. Furthermore, Indigo also does not distinguish between
various transaction isolation guarantees, which \name does.

@@

Several conditions have been proposed to judge whether an operation on a
replicated data object needs coordination or not. ~\cite{Calm} defines
\emph{logical monotonicity} as a sufficient condition for coordination freedom,
and proposes a consistency analysis that marks code regions performing
non-monotonic reasoning (eg: aggregations, such as \cf{COUNT}) as potential
coordination points. ~\cite{IConfluence} and ~\cite{Sieve} define
\emph{invariant confluence} and \emph{invariant safety}, respectively, as
conditions for safely executing an operation without coordination.
~\cite{Sieve} also proposes a program analysis that conservatively marks
certain operations as \emph{blue} (coordination not required), while marking
the remaining as \emph{red} (coordination required). Unlike \name, these works
focus on a coarse-grained classification of consistency as eventual or strong,
and do not focus on finer-grained transaction isolation levels. However, the
analyses they propose relieve programmers of the burden to tag operations with
consistency levels. Indeed, we do consider automatic inference of consistency
contracts from application-specific integrity constraints as the next step for
\name.

>>>>

Since eventual consistency alone is insufficient to build correct applications,
several systems~\cite{Bayou,Pileus,RedBlue} propose a lattice of stronger
consistency levels. Similarly, traditional database processing
systems~\cite{Berenson95} and their replicated variants~\cite{BailisHAT}
propose weaker isolation levels for performance. In these systems, the onus is
on the developer to choose the correct consistency(isolation) level for
operations(transactions). \name relieves the developer of this burden, and
instead expects  contracts expressing declarative visibility requirements.

@@

Several conditions have been proposed to judge whether an operation on a
replicated data object needs coordination or not. ~\cite{Calm} defines
\emph{logical monotonicity} as a sufficient condition for coordination freedom,
and proposes a consistency analysis that marks code regions performing
non-monotonic reasoning (eg: aggregations, such as \cf{COUNT}) as potential
coordination points. ~\cite{IConfluence} and ~\cite{Sieve} define
\emph{invariant confluence} and \emph{invariant safety}, respectively, as
conditions for safely executing an operation without coordination.
~\cite{Sieve} also proposes a program analysis that conservatively marks certain
operations as \emph{blue} (coordination not required), while marking the
remaining as \emph{red} (coordination required). ~\cite{indigo} requires
programmers to declare application semantics, and the desired
application-specific invariants as formulas in first-order logic. It performs
static analysis on these formulas to determine $I$-offender sets - sets of
operations, which, when performed concurrently, result in violation of one or
more of the stated invariants. For each offending set of operation, if
programmer chooses invariant-violation avoidance over violation repair, the
system employs various techniques, such as escrow reservation, to ensure that
the offending set of operations are effectively serialized. Unlike \name, these
works focus on a coarse-grained classification of consistency as eventual or
strong, and do not focus on finer-grained transaction isolation levels. However,
the analyses that some of them propose relieve programmers of the burden to tag
operations with consistency levels. Indeed, we do consider automatic inference
of consistency contracts from application-specific integrity constraints as the
next step for \name.
